---
title: "ia_study1_suppleAnalyses"
author: "Verity Y. Q. Lua"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

\newpage

```{r setup, message = FALSE}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(emmeans)
library(psych)
library(patchwork)
library(lme4)
library(lmerTest)
source("https://raw.githubusercontent.com/vyqlua/avi_functions/refs/heads/main/ipsatize_fn.R")
```

```{r create list for specifying arguments to filter additional exclusion criteria easily}
sensitivity_analyses <- c("!is.na(subID)", "exclude_sd != 1")
```

```{r set ggplot common theme, include = FALSE}

theme_myplot <- theme_minimal(base_size = 12) +
  theme(
    plot.background  = element_rect(fill = "white", color = NA),
    panel.grid       = element_blank(),
    axis.line        = element_line(color = "black"),
    axis.title       = element_text(face = "bold"),
    legend.title     = element_text(face = "bold"),
    legend.position  = "right",
    legend.background = element_rect(fill = "white", color = "black"),
    strip.text       = element_text(face = "bold")
  )

theme_set(theme_myplot)

```

```{r define aov_analysis fn}
# Define AOV analysis function

aov_analysis <- 
  function(formula, data, filter_condition1, filter_condition2 = NULL) 
    {
    # Initialize a list to store results from each iteration
    analysis_result <- list()
  if (is.null(filter_condition2)) {
    for (i in 1:length(filter_condition1)) {
      subset_data <- data %>% 
        filter(eval(parse(text = filter_condition1[i])))
    # Run the analysis on the subset
    analysis_result[[filter_condition1[i]]] <- 
      aov(formula, data = subset_data) %>% summary()
    }}
  else {
    for (j in 1:length(filter_condition2)) {
      for (i in 1:length(filter_condition1)) {
        subset_data <- data %>% 
          filter(eval(parse(text = filter_condition1[i]))) %>%
          filter(eval(parse(text = filter_condition2[j])))
    # Run the analysis on the subset
    analysis_result[[
      paste(filter_condition1[i], "&", filter_condition2[j])]] <- 
      aov(formula = formula, data = subset_data) %>% summary()
      }}
    }
  return(analysis_result)
}

```

\newpage

# Load Data

```{r load data, message = FALSE}
data <- read_csv("ia_study1_anon_data_computed.csv")
data <- data[ , -1]

levelBreakdown <- read_csv("ia_TrialsBreakdown.csv")
```

\newpage

## Convert data to long data

```{r convert giving data to long form ip}
# convert giving data into long form
longGivingdata_i <- data %>% 
  dplyr::select(
    subID, cultureEA, order,
    starts_with("raw") & contains("_i"),
    starts_with("exclude"),
    age # covariates 
    ) %>%
  pivot_longer(
    cols = `raw1_i`:`raw36_i`, 
    names_to = "trial",
    values_to = "response_i") %>%
  dplyr::mutate(
    trial = as.numeric(substr(trial, start = 4, stop = str_length(trial)-2)))
```

```{r attach trial information ip}
# add info on incidental affect (mood), face gender, face race, and face emotion for each trial.
longGivingdata_i = longGivingdata_i %>% 
  dplyr::mutate(
    mood = levelBreakdown$mood[trial],
    faceGender = levelBreakdown$faceGender[trial], 
    faceRace = levelBreakdown$faceRace[trial], 
    faceEmotion = levelBreakdown$faceEmotion[trial])

# make variables factors
longGivingdata_i = longGivingdata_i %>% 
  dplyr::mutate(
    culture = ifelse(cultureEA == 1, "EA", "TN") %>% as.factor(),
    mood = factor(mood, levels = c("HAP", "HAN","Neutral")),
    faceRace = factor(faceRace, levels = c("White", "Asian")),
    faceGender = factor(faceGender, levels = c("Male", "Female")),
    faceEmotion = factor(faceEmotion, levels = c("Excited", "Calm", "Neutral")),
    subID = factor(subID, unique(subID)))

longGivingdata_i = longGivingdata_i %>% 
  dplyr::filter(!is.na(response_i),
                !is.na(age))
```

```{r convert giving data to long form}
# convert AVI data into long form
longGivingdata <- data %>% 
  dplyr::select(
    subID, cultureEA, order,
    starts_with("raw") & !contains("_i") & !contains("Page"),
    starts_with("exclude"),
    age # covariates 
    ) %>%
  pivot_longer(
    cols = `raw1`:`raw36`, 
    names_to = "trial",
    values_to = "response") %>%
  dplyr::mutate(
    trial = as.numeric(substr(trial, start = 4, stop = str_length(trial))))
```

```{r attach trial information}
# add info on incidental affect (mood), face gender, face race, and face emotion for each trial.
longGivingdata = longGivingdata %>% 
  dplyr::mutate(
    mood = levelBreakdown$mood[trial],
    faceGender = levelBreakdown$faceGender[trial], 
    faceRace = levelBreakdown$faceRace[trial], 
    faceEmotion = levelBreakdown$faceEmotion[trial])

# make variables factors
longGivingdata = longGivingdata %>% 
  dplyr::mutate(
    culture = ifelse(cultureEA == 1, "EA", "TN") %>% as.factor(),
    mood = factor(mood, levels = c("HAP", "HAN","Neutral")),
    faceRace = factor(faceRace, levels = c("White", "Asian")),
    faceGender = factor(faceGender, levels = c("Male", "Female")),
    faceEmotion = factor(faceEmotion, levels = c("Excited", "Calm", "Neutral")),
    subID = factor(subID, unique(subID)))

longGivingdata = longGivingdata %>% dplyr::filter(!is.na(response))
```

\newpage

## Attach AVI data to giving data

```{r merge baseline to giving data}

baseAVIdata <- 
  data %>%
  dplyr::select(subID, cultureEA, 
                exclude_age, exclude_sd, 
                gender, age, sexualpref, 
                rHAP, rLAP, rHAN, rLAN,
                iHAP, iLAP, iHAN, iLAN,
                rMaxPos, iMaxPos,
                rHAP_i, rLAP_i, rHAN_i, rLAN_i,
                iHAP_i, iLAP_i, iHAN_i, iLAN_i,
                rMaxPos_i, iMaxPos_i,
                avatar_ori) %>%
  dplyr::mutate(
    avatar_ori = case_when(
      avatar_ori == "1-a" ~ "FAN",
      avatar_ori == "1-b" ~ "FAE",
      avatar_ori == "1-c" ~ "FAC",
      avatar_ori == "2-a" ~ "MWE",
      avatar_ori == "2-b" ~ "MWC",
      avatar_ori == "2-c" ~ "MWN",
      avatar_ori == "3-a" ~ "MAN",
      avatar_ori == "3-b" ~ "MAC",
      avatar_ori == "3-c" ~ "MAE",
      avatar_ori == "4-a" ~ "FWN",
      avatar_ori == "4-b" ~ "FWC",
      avatar_ori == "4-c" ~ "FWE")) %>%
  separate_wider_position(
    avatar_ori,
    widths = c(
      avatar_gender = 1,
      avatar_race = 1,
      avatar_expression = 1
    )) %>%
  dplyr::mutate(
    avatar_gender = factor(avatar_gender,
                           levels = c("M", "F"),
                           labels = c("Male", "Female")),
    avatar_race = factor(avatar_race,
                         levels = c("W", "A"),
                         labels = c("White", "Asian")), 
    avatar_expression = factor(avatar_expression,
                               levels = c("E", "C", "N"),
                               labels = c("Excited", "Calm", "Neutral")))

longGivingdata <- 
  left_join(longGivingdata,
            baseAVIdata %>% 
              dplyr::select(subID:sexualpref,
                            avatar_gender, avatar_race, avatar_expression,
                            rHAP:iMaxPos),
            by = intersect(
              colnames(longGivingdata), 
              colnames(baseAVIdata)))


longGivingdata_i <- 
  left_join(longGivingdata_i,
            baseAVIdata %>% 
              dplyr::select(subID:sexualpref,
                            avatar_gender, avatar_race, avatar_expression,
                            rHAP_i:iMaxPos_i),
            by = intersect(
              colnames(longGivingdata_i), 
              colnames(baseAVIdata)))

```

## Attach trait dating data to giving data

```{r convert trait rating data to long form}

# convert trait rating data into long form
traitRatingsdata <- data %>% 
  dplyr::select(
    subID, cultureEA, order,
    starts_with("exclude"),
    starts_with("trait") & !contains("Mean") & !contains("Sd"),
    starts_with("vale") & !contains("Mean") & !contains("Sd"),
    starts_with("arou") & !contains("Mean") & !contains("Sd")) %>%
  pivot_longer(
    cols = `trait1_Competent`:`arou18_i`, 
    names_to = "rating",
    values_to = "response") %>%
  dplyr::mutate(rating_no = as.numeric(str_extract_all(rating, "[0-9]+")))

# add info on face gender, face race, and face emotion for each rating
traitRatingsdata <- traitRatingsdata %>% 
  dplyr::mutate(
    trial = ifelse(order == 1 | order == 3, 
                   rating_no, 
                   36-rating_no+1),
    faceGender = ifelse(order == 1 | order == 3, 
                        levelBreakdown$faceGender[rating_no], 
                        levelBreakdown$faceGender[36-rating_no+1]),
    faceRace = ifelse(order == 1 | order == 3, 
                      levelBreakdown$faceRace[rating_no], 
                      levelBreakdown$faceRace[36-rating_no+1]),
    faceEmotion = ifelse(order == 1 | order == 3, 
                         levelBreakdown$faceEmotion[rating_no], 
                         levelBreakdown$faceEmotion[36-rating_no+1]))

# make variables factors
traitRatingsdata = traitRatingsdata %>% 
  dplyr::mutate(
    culture = ifelse(
      cultureEA == 1, "EA", "TN") %>% as.factor(),
    faceRace = factor(
      faceRace, levels = c("White", "Asian")),
    faceGender = factor(
      faceGender, levels = c("Male", "Female")),
    faceEmotion = factor(
      faceEmotion, levels = c("Excited", "Calm", "Neutral", "Negative")),
    subID = factor(
      subID, unique(subID)))

# convert data back into wide form
traitRatingsdata <- traitRatingsdata %>% 
  dplyr::mutate(
    rating = str_replace(rating, "trait[1-9][0-9]*_", ""),
    rating = str_replace(rating, "vale[1-9][0-9]*", "Valence"),
    rating = str_replace(rating, "arou[1-9][0-9]*", "Arousal")) %>%
  pivot_wider(
    id_cols = c("subID", "culture", "cultureEA", "order", "trial", "rating_no",
                "exclude_age", "exclude_sd", 
                "faceRace", "faceGender", "faceEmotion"),
    names_from = "rating",
    values_from = "response")

```

```{r merge trait ratings with giving data}

longGivingdata <-
  left_join(
    longGivingdata,
    traitRatingsdata %>% 
      dplyr::select(subID:faceEmotion,
                    Competent:aGoodPerson,
                    Valence, Arousal),
    by = intersect(colnames(longGivingdata), colnames(traitRatingsdata))
  ) %>%
  dplyr::mutate( 
    culture = ifelse(cultureEA == 1, "EA", "TN") %>% as.factor())

```

```{r merge trait ratings with giving data ip}

longGivingdata_i <-
  left_join(
    longGivingdata_i,
    traitRatingsdata %>% 
      dplyr::select(subID:faceEmotion,
                    Competent_i:aGoodPerson_i,
                    Valence_i, Arousal_i),
    by = intersect(colnames(longGivingdata_i), colnames(traitRatingsdata))
  ) %>%
  dplyr::mutate( 
    culture = ifelse(cultureEA == 1, "EA", "TN") %>% as.factor())

```

\newpage

# Supple For: Are There Cultural Differences in Ideal Affect between European Americans and Taiwanese?

## Raw Ideal Affect Scores

```{r plot AVI}
plot_avi(data, group_id = "cultureEA", ipsatized_only = FALSE)
```

\newpage

# Supple For: Does Induced Mood Influence Giving Towards Excited, Calm, and Neutral Responders Differently Across Cultures?

## Ipsatized Giving Controlling for Age

### Sample size

```{r sample size main ip}
print("n_total:"); longGivingdata_i %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata_i %>%
  dplyr::filter(culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata_i %>%
  dplyr::filter(culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```

\newpage

### Visualizations

Same as main analyses, hence not plotted

### Analyses

```{r main three-way analysis}

aov(
  formula = response_i ~ mood*culture*faceEmotion + mood*age*faceEmotion +
    Error(subID/(mood*faceEmotion)),
  data = longGivingdata_i) %>% summary()

```

\newpage

#### Pairwise

```{r pairwise analyses}
pairwise <- aov(
  formula = response_i ~ mood*culture*faceEmotion + mood*age*faceEmotion +
    Error(subID/(mood*faceEmotion)),
  data = longGivingdata_i) 
```

Main effect mood
```{r pairwise main effect mood}
# main effect mood
emm_3way_mood <- emmeans(pairwise, ~ mood) 
pairs(emm_3way_mood) # p values
#confint(pairs(emm_3way_mood)) # confidence intervals
```

Main effect faceEmotion
```{r pairwise main effect faceEmotion}
# main effect faceEmotion
emm_3way_faceEmotion <- emmeans(pairwise, ~ faceEmotion)
pairs(emm_3way_faceEmotion) # p values
#confint(pairs(emm_3way_faceEmotion)) # confidence intervals
```

\newpage

Culture:faceEmotion
```{r pairwise Culture:faceEmotion}
emm_3way_faceEmotionCulture <- emmeans(pairwise, ~ culture | faceEmotion) 
pairs(emm_3way_faceEmotionCulture) # p values
#confint(pairs(emm_3way_faceEmotionCulture)) # confidence intervals
```

Mood:faceEmotion
```{r pairwise Mood:faceEmotion}
emm_3way_faceEmotionMood <- emmeans(pairwise, ~ faceEmotion | mood) 
pairs(emm_3way_faceEmotionMood) # p values
#confint(pairs(emm_3way_faceEmotionMood)) # confidence intervals
```

\newpage

Mood:culture:faceEmotion

```{r pairwise Mood:culture:faceEmotion bymood}
emm_3way_bymood <- emmeans(pairwise, ~ culture * faceEmotion | mood) 
pairs(emm_3way_bymood) # p values
#confint(pairs(emm_3way_bymood)) # confidence intervals
```

```{r pairwise Mood:culture:faceEmotion byfaceEmotion}
emm_3way_byfaceEmotion <- emmeans(pairwise, ~ culture * mood | faceEmotion) 
pairs(emm_3way_byfaceEmotion) # p values
#confint(pairs(emm_3way_byfaceEmotion)) # confidence intervals
```

\newpage

## Raw Giving Scores

### Sample size

1. Supple analyses (!is.na(subID)) - Includes all participants

```{r sample size main}
print("n_total:"); longGivingdata %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata %>%
  dplyr::filter(culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata %>%
  dplyr::filter(culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```

2. Supple analyses (exclude_sd != 1) - Excludes participants who gave equally to all targets

```{r sample size exclude sd}
print("n_total:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1) %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1, culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1, culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```

\newpage

### Visualizations

1. Supple analyses (!is.na(subID)) - Includes all participants

```{r plot three-way (!is.na(subID)), message = FALSE, fig.width = 10, fig.height = 7}

longGivingdata2 <- longGivingdata %>% dplyr::mutate(
  culture = if_else(culture == "EA", "European American", "Taiwanese")) %>%
  dplyr::rename(Culture = culture) %>%
  dplyr::mutate(
    mood = factor(mood,
                  labels = c("Neutral", "HAP", "HAN"),
                  levels = c("Neutral", "HAP", "HAN")))
ggplot(
  longGivingdata2 %>% 
    group_by(subID, mood, faceEmotion, Culture) %>% 
    summarise(response = mean(response, na.rm = T)) %>%
    group_by(faceEmotion, mood, Culture) %>%
    summarise(mean = mean(response, na.rm = T),
              SD = sd(response, na.rm = T),
              SE = sd(response, na.rm = T)/sqrt(n())), 
  aes(faceEmotion, mean, fill = Culture)) + 
  facet_grid(~mood)+
  scale_fill_manual(
    values = c("European American"="#F49070", "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1)+
  xlab("Facial Expression") +
  ylab("Amount Given (Raw)") +
  ggtitle("Amount Given by Mood Condition and Responder's Facial Expression") 

```

```{r plot two-ways (!is.na(subID)), message = FALSE, fig.width = 10, fig.height = 12}

p1 <- ggplot(longGivingdata2 %>%
               group_by(subID, mood, Culture) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(mood, Culture) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(mood, mean, fill = Culture)) + 
  scale_fill_manual(values = 
                      c("European American"="#F49070", 
                        "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Mood") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by Mood Condition") 

p2 <- ggplot(longGivingdata2 %>%
               group_by(subID, faceEmotion, Culture) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(faceEmotion, Culture) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(faceEmotion, mean, fill = Culture)) + 
  scale_fill_manual(values = 
                      c("European American"="#F49070", 
                        "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Facial Expression") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by faceEmotion Condition") 

p3 <- ggplot(longGivingdata2 %>%
               group_by(subID, faceEmotion, mood) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(faceEmotion, mood) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(mood, mean, fill = faceEmotion)) + 
  scale_fill_manual(values = 
                      c("Neutral"="grey", 
                        "Excited"="lightyellow",
                        "Calm"="lightblue")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Mood") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by faceEmotion Condition") 

p1 + p2 + p3 +
  patchwork::plot_layout(
    ncol = 1
  )

```

```{r clean env longGivingdata2, include = FALSE}
rm(longGivingdata2, p1, p2, p3)
```

2. Supple analyses (exclude_sd != 1) - Excludes participants who gave equally to all targets

```{r plot three-way (exclude_sd), message = FALSE, fig.width = 10, fig.height = 7}

longGivingdata2a <- longGivingdata %>% 
  dplyr::filter(exclude_sd != 1) %>%
  dplyr::mutate(
  culture = if_else(culture == "EA", "European American", "Taiwanese")) %>%
  dplyr::rename(Culture = culture) %>%
  dplyr::mutate(
    mood = factor(mood,
                  labels = c("Neutral", "HAP", "HAN"),
                  levels = c("Neutral", "HAP", "HAN")))
ggplot(
  longGivingdata2a %>% 
    group_by(subID, mood, faceEmotion, Culture) %>% 
    summarise(response = mean(response, na.rm = T)) %>%
    group_by(faceEmotion, mood, Culture) %>%
    summarise(mean = mean(response, na.rm = T),
              SD = sd(response, na.rm = T),
              SE = sd(response, na.rm = T)/sqrt(n())), 
  aes(faceEmotion, mean, fill = Culture)) + 
  facet_grid(~mood)+
  scale_fill_manual(
    values = c("European American"="#F49070", "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1)+
  xlab("Facial Expression") +
  ylab("Amount Given (Raw)") +
  ggtitle("Amount Given by Mood Condition and Responder's Facial Expression") 

```

```{r plot two-ways (exclude_sd), message = FALSE, fig.width = 10, fig.height = 12}

p1 <- ggplot(longGivingdata2a %>%
               group_by(subID, mood, Culture) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(mood, Culture) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(mood, mean, fill = Culture)) + 
  scale_fill_manual(values = 
                      c("European American"="#F49070", 
                        "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Mood") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by Mood Condition") 

p2 <- ggplot(longGivingdata2a %>%
               group_by(subID, faceEmotion, Culture) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(faceEmotion, Culture) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(faceEmotion, mean, fill = Culture)) + 
  scale_fill_manual(values = 
                      c("European American"="#F49070", 
                        "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Facial Expression") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by faceEmotion Condition") 

p3 <- ggplot(longGivingdata2a %>%
               group_by(subID, faceEmotion, mood) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(faceEmotion, mood) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(mood, mean, fill = faceEmotion)) + 
  scale_fill_manual(values = 
                      c("Neutral"="grey", 
                        "Excited"="lightyellow",
                        "Calm"="lightblue")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Mood") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by faceEmotion Condition") 

p1 + p2 + p3 +
  patchwork::plot_layout(
    ncol = 1
  )

```

```{r clean env longGivingdata2a, include = FALSE}
rm(longGivingdata2a, p1, p2, p3)
```


\newpage

### Analyses

```{r main three-way analysis raw giving}

aov_analysis(
  formula = response ~ mood*culture*faceEmotion + 
    Error(subID/(mood*faceEmotion)),
  data = longGivingdata,
  filter_condition1 = sensitivity_analyses)

```

\newpage

#### Pairwise (Raw Giving, !is.na(subID))

```{r pairwise analyses (Raw Giving, !is.na(subID))}
pairwise <- aov(
  formula = response ~ mood*culture*faceEmotion + 
    Error(subID/(mood*faceEmotion)),
  data = longGivingdata)
```

Mood:culture:faceEmotion

```{r pairwise Mood:culture:faceEmotion bymood (Raw Giving, !is.na(subID))}
emm_3way_bymood <- emmeans(pairwise, ~ culture * faceEmotion | mood) 
pairs(emm_3way_bymood) # p values
#confint(pairs(emm_3way_bymood)) # confidence intervals
```

```{r pairwise Mood:culture:faceEmotion byfaceEmotion (Raw Giving, !is.na(subID))}
emm_3way_byfaceEmotion <- emmeans(pairwise, ~ culture * mood | faceEmotion) 
pairs(emm_3way_byfaceEmotion) # p values
#confint(pairs(emm_3way_byfaceEmotion)) # confidence intervals
```

\newpage

#### Pairwise (Raw Giving, exclude_sd != 1)

```{r pairwise analyses (Raw Giving, exclude_sd}
pairwise <- aov(
  formula = response ~ mood*culture*faceEmotion + 
    Error(subID/(mood*faceEmotion)),
  data = longGivingdata %>% 
    dplyr::filter(exclude_sd != 1))
```

Mood:culture:faceEmotion

```{r pairwise Mood:culture:faceEmotion bymood (Raw Giving, exclude_sd}
emm_3way_bymood <- emmeans(pairwise, ~ culture * faceEmotion | mood) 
pairs(emm_3way_bymood) # p values
#confint(pairs(emm_3way_bymood)) # confidence intervals
```

```{r pairwise Mood:culture:faceEmotion byfaceEmotion (Raw Giving, exclude_sd)}
emm_3way_byfaceEmotion <- emmeans(pairwise, ~ culture * mood | faceEmotion) 
pairs(emm_3way_byfaceEmotion) # p values
#confint(pairs(emm_3way_byfaceEmotion)) # confidence intervals
```

```{r clean environment, include = FALSE}

rm(emm_3way_mood, emm_3way_byfaceEmotion, emm_3way_bymood, 
   emm_3way_faceEmotion, emm_3way_faceEmotionCulture, emm_3way_faceEmotionMood,
   pairwise)

```

\newpage


## Using Ideal Affect as Moderator

### Sample size

```{r sample size main ip ideal affect}
print("n_total:"); longGivingdata_i %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata_i %>%
  dplyr::filter(culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata_i %>%
  dplyr::filter(culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```

\newpage

### Visualizations

```{r plot three-way iMaxPos_i, message = FALSE, fig.width = 10, fig.height = 12}

p1 <- ggplot(longGivingdata_i,
       aes(x = iMaxPos_i, y = response_i)) +
  facet_grid(~ faceEmotion) +
  geom_point(alpha = .3, aes(color = culture)) +
  geom_smooth(method = "lm", se = TRUE) +
  xlab("iMaxPos_i") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by iMaxPos_i and Responder's Facial Expression")

p2 <- ggplot(longGivingdata_i,
       aes(x = iMaxPos_i, y = response_i)) +
  facet_grid(~ mood) +
  geom_point(alpha = .3, aes(color = culture)) +
  geom_smooth(method = "lm", se = TRUE) +
  xlab("iMaxPos_i") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by iMaxPos_i and Mood")

p1 + p2 +
  patchwork::plot_layout(
    ncol = 1
  )
  
```

\newpage

Remove outliers

```{r plot three-way iMaxPos_i rm outliers, message = FALSE, fig.width = 10, fig.height = 12}

longGivingdata_i_rmOUT <- 
  longGivingdata_i %>%
  dplyr::filter(
    iMaxPos_i > mean(iMaxPos_i) - 3*sd(iMaxPos_i),
    iMaxPos_i < mean(iMaxPos_i) + 3*sd(iMaxPos_i)
  )

# sample size

longGivingdata_i_rmOUT %>% 
  distinct(subID, .keep_all = TRUE) %>%
  dplyr::select(culture) %>%
  table()

p1 <- ggplot(longGivingdata_i_rmOUT,
       aes(x = iMaxPos_i, y = response_i)) +
  facet_grid(~ faceEmotion) +
  geom_point(alpha = .3, aes(color = culture)) +
  geom_smooth(method = "lm", se = TRUE) +
  xlab("iMaxPos_i") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by iMaxPos_i and Responder's Facial Expression")

p2 <- ggplot(longGivingdata_i_rmOUT,
       aes(x = iMaxPos_i, y = response_i)) +
  facet_grid(~ mood) +
  geom_point(alpha = .3, aes(color = culture)) +
  geom_smooth(method = "lm", se = TRUE) +
  xlab("iMaxPos_i") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by iMaxPos_i and Mood")

p1 + p2 +
  patchwork::plot_layout(
    ncol = 1
  )
  
```

```{r clean env iMaxPos Giving, include = FALSE}

rm(longGivingdata_i_rmOUT, p1, p2)

```

\newpage

### Three-Way Analyses

```{r main three-way analysis ideal affect maxpos}

lmer(
  formula = response_i ~ mood*iMaxPos_i*faceEmotion + 
    rMaxPos_i +
    (1 | mood),
  data = longGivingdata_i) %>% summary()

```

\newpage

### Within Neu Mood Analyses

```{r analysis within neu mood ideal affect}

lmer(
  formula = response_i ~ iHAP_i*faceEmotion + iLAP_i*faceEmotion +
    rHAP_i + rLAP_i +
    (1 | faceEmotion),
  data = longGivingdata_i %>%
    dplyr::filter(
      mood == "Neutral"
    )) %>% summary()

```

\newpage

# Other analyses

## Avatar choosen

### Visualizations
            
Avatar choosen

```{r plot choosen avatar, echo = FALSE, fig.width = 10, fig.height = 11}

p1 <- ggplot(
  longGivingdata %>%
    distinct(subID, .keep_all = TRUE) %>%
    group_by(culture) %>%
    summarize(
      Male = sum(avatar_gender == "Male"),
      Female = sum(avatar_gender == "Female"),
      .groups = "drop"
    ) %>%
    pivot_longer(c(Male, Female),
                 names_to = "avatar_gender",
                 values_to = "count"),
  aes(x = culture, y = count, fill = avatar_gender)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("Male"="lightblue", "Female"="pink")) 

p2 <- ggplot(
  longGivingdata %>%
    distinct(subID, .keep_all = TRUE) %>%
    group_by(culture) %>%
    summarize(
      White = sum(avatar_race == "White"),
      Asian = sum(avatar_race == "Asian"),
      .groups = "drop"
    ) %>%
    pivot_longer(c(White, Asian),
                 names_to = "avatar_race",
                 values_to = "count"),
  aes(x = culture, y = count, fill = avatar_race)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("White"="#F49070", "Asian"="#52B2CF")) 

p3 <- ggplot(
  longGivingdata %>%
    distinct(subID, .keep_all = TRUE) %>%
    group_by(culture) %>%
    summarize(
      Excited = sum(avatar_expression == "Excited"),
      Calm = sum(avatar_expression == "Calm"),
      Neutral = sum(avatar_expression == "Neutral"),
      .groups = "drop"
    ) %>%
    pivot_longer(c(Excited, Calm, Neutral),
                 names_to = "avatar_expression",
                 values_to = "count"),
  aes(x = culture, y = count, fill = avatar_expression)) +
  geom_col(position = "dodge") + 
  scale_fill_manual(values = 
                      c("Neutral"="grey", 
                        "Excited"="lightyellow",
                        "Calm"="lightblue"))

p1 + p2 + p3 +
  patchwork::plot_layout(
    ncol = 1
  )

```

```{r clean environment plots, include = FALSE}

rm(p1, p2, p3)

```

\newpage

Avatar choosen congruence

```{r avatar gender congruence, fig.width = 10, fig.height = 5}

ggplot(
  longGivingdata %>%
    distinct(subID, .keep_all = TRUE) %>%
    group_by(culture, gender) %>%
    summarize(
      n = n(),
      Male = sum(avatar_gender == "Male"),
      Female = sum(avatar_gender == "Female"),
      .groups = "drop"
    ) %>%
    dplyr::mutate(
      Male = Male/n,
      Female = Female/n) %>%
    pivot_longer(c(Male, Female),
                 names_to = "avatar_gender",
                 values_to = "count"),
  aes(x = culture, y = count, fill = avatar_gender)) +
  geom_col(position = "dodge") +
  facet_wrap(~ gender) +
  ylim(0,1) +
  scale_fill_manual(values = c("Male"="lightblue", "Female"="pink")) 

```

```{r avatar race congruence, fig.width = 10, fig.height = 5}

ggplot(
  longGivingdata %>%
    distinct(subID, .keep_all = TRUE) %>%
    group_by(culture) %>%
    summarize(
      n = n(),
      White = sum(avatar_race == "White"),
      Asian = sum(avatar_race == "Asian"),
      .groups = "drop"
    ) %>%
    dplyr::mutate(
      White = White/n,
      Asian = Asian/n) %>%
    pivot_longer(c(White, Asian),
                 names_to = "avatar_race",
                 values_to = "count"),
  aes(x = culture, y = count, fill = avatar_race)) +
  geom_col(position = "dodge") +
  ylim(0,1) +
  scale_fill_manual(values = c("White"="#F49070", "Asian"="#52B2CF")) 

```

\newpage

## Trait ratings

### Visualizations

Raw Ratings
                                                   
```{r plot trait ratings of faces raw, echo = FALSE, fig.width = 10, fig.height = 12}

vars <- c(
  'Valence', 'Arousal', 'aGoodPerson',
  'Friendly', 'Competent', 'Trustworthy', 
  'Dominant', 'FinanciallyNeedy', 'Selfish')

plot_data <- 
  longGivingdata %>%
  pivot_longer(
    all_of(vars), names_to = "trait", values_to = "rating") %>%
  group_by(subID, faceEmotion, culture, trait) %>%
  summarise(rating = mean(rating, na.rm = TRUE), .groups="drop") %>%
  group_by(faceEmotion, culture, trait) %>%
  summarise(
    mean = mean(rating, na.rm = TRUE),
    SD = sd(rating, na.rm = TRUE),
    SE = SD/sqrt(n()),
    .groups="drop"
  ) %>%
  dplyr::mutate(
    trait = factor(trait, levels = vars))

ggplot(plot_data, aes(faceEmotion, mean, fill = culture)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(
    aes(ymin = mean-SE, ymax = mean+SE),
    position = position_dodge(0.9), width = 0.1
  ) +
  geom_hline(yintercept = 4, linetype = "dotted") +
  scale_fill_manual(values = c("EA"="#F49070", "TN"="#52B2CF")) +
  facet_wrap(~ trait, ncol = 3) +
  xlab("Facial Expression") +
  ylab("Rating (Raw)") +
  ggtitle("Trait Ratings by Responder's Facial Expression")

```

\newpage

Ipsatized Ratings
                                                   
```{r plot trait ratings of faces ip, echo = FALSE, fig.width = 10, fig.height = 12}

vars <- c(
  'Valence_i', 'Arousal_i', 'aGoodPerson_i',
  'Friendly_i', 'Competent_i', 'Trustworthy_i', 
  'Dominant_i', 'FinanciallyNeedy_i', 'Selfish_i')

plot_data_i <- 
  longGivingdata_i %>%
  pivot_longer(
    all_of(vars), names_to = "trait", values_to = "rating") %>%
  group_by(subID, faceEmotion, culture, trait) %>%
  summarise(rating = mean(rating, na.rm = TRUE), .groups="drop") %>%
  group_by(faceEmotion, culture, trait) %>%
  summarise(
    mean = mean(rating, na.rm = TRUE),
    SD = sd(rating, na.rm = TRUE),
    SE = SD/sqrt(n()),
    .groups="drop"
  ) %>%
  dplyr::mutate(
    trait = factor(trait, levels = vars))

ggplot(plot_data_i, aes(faceEmotion, mean, fill = culture)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(
    aes(ymin = mean-SE, ymax = mean+SE),
    position = position_dodge(0.9), width = 0.1
  ) +
  scale_fill_manual(values = c("EA"="#F49070", "TN"="#52B2CF")) +
  facet_wrap(~ trait, ncol = 3) +
  xlab("Facial Expression") +
  ylab("Rating (Ipsatized)") +
  ggtitle("Trait Ratings by Responder's Facial Expression")

```
