---
title: "ia_study1_suppleAnalyses"
author: "Verity Y. Q. Lua"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, message = FALSE}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(emmeans)
library(psych)
library(patchwork)
source("https://raw.githubusercontent.com/vyqlua/avi_functions/refs/heads/main/ipsatize_fn.R")
```

```{r create list for specifying arguments to filter additional exclusion criteria easily}
sensitivity_analyses <- c("!is.na(subID)",
  "exclude_age != 1", "exclude_sd != 1", 
  "exclude_age != 1 & exclude_sd != 1")
sensitivity_analyses_i <- c("!is.na(subID)", "exclude_age != 1")
```

```{r set ggplot common theme, include = FALSE}

theme_myplot <- theme_minimal(base_size = 12) +
  theme(
    plot.background  = element_rect(fill = "white", color = NA),
    panel.grid       = element_blank(),
    axis.line        = element_line(color = "black"),
    axis.title       = element_text(face = "bold"),
    legend.title     = element_text(face = "bold"),
    legend.position  = "right",
    legend.background = element_rect(fill = "white", color = "black"),
    strip.text       = element_text(face = "bold")
  )

theme_set(theme_myplot)

```


\newpage

# Load Data

```{r load data, message = FALSE}
data <- read_csv("ia_study1_anon_data_computed.csv")
data <- data[ , -1]

levelBreakdown <- read_csv("ia_TrialsBreakdown.csv")
```

\newpage

# Raw Ideal Affect: Are There Cultural Differences in Ideal Affect between European Americans and Taiwanese?

```{r plot AVI}

#plot_avi(data, group_id = "cultureEA")
#need to figure out what affective states to include in AVI measure

```

\newpage

# Raw Giving: Does Induced Mood Influence Giving Towards Excited, Calm, and Neutral Responders Differently Across Cultures?

## Admin before analyses

```{r define aov_analysis fn}
# Define the analysis function

aov_analysis <- 
  function(formula, data, filter_condition1, filter_condition2 = NULL) 
    {
    # Initialize a list to store results from each iteration
    analysis_result <- list()
  if (is.null(filter_condition2)) {
    for (i in 1:length(filter_condition1)) {
      subset_data <- data %>% 
        filter(eval(parse(text = filter_condition1[i])))
    # Run the analysis on the subset
    analysis_result[[filter_condition1[i]]] <- 
      aov(formula, data = subset_data) %>% summary()
    }}
  else {
    for (j in 1:length(filter_condition2)) {
      for (i in 1:length(filter_condition1)) {
        subset_data <- data %>% 
          filter(eval(parse(text = filter_condition1[i]))) %>%
          filter(eval(parse(text = filter_condition2[j])))
    # Run the analysis on the subset
    analysis_result[[
      paste(filter_condition1[i], "&", filter_condition2[j])]] <- 
      aov(formula = formula, data = subset_data) %>% summary()
      }}
    }
  return(analysis_result)
}

```

```{r convert giving data to long form}
# convert AVI data into long form
longGivingdata <- data %>% 
  dplyr::select(
    subID, cultureEA, order,
    starts_with("raw") & !contains("_i") & !contains("Page"),
    starts_with("exclude"),
    age # covariates 
    ) %>%
  pivot_longer(
    cols = `raw1`:`raw36`, 
    names_to = "trial",
    values_to = "response") %>%
  dplyr::mutate(
    trial = as.numeric(substr(trial, start = 4, stop = str_length(trial))))
```

```{r attach trial information}
# add info on incidental affect (mood), face gender, face race, and face emotion for each trial.
longGivingdata = longGivingdata %>% 
  dplyr::mutate(
    mood = levelBreakdown$mood[trial],
    faceGender = levelBreakdown$faceGender[trial], 
    faceRace = levelBreakdown$faceRace[trial], 
    faceEmotion = levelBreakdown$faceEmotion[trial])

# make variables factors
longGivingdata = longGivingdata %>% 
  dplyr::mutate(
    culture = ifelse(cultureEA == 1, "EA", "TN") %>% as.factor(),
    mood = factor(mood, levels = c("HAP", "HAN","Neutral")),
    faceRace = factor(faceRace, levels = c("White", "Asian")),
    faceGender = factor(faceGender, levels = c("Male", "Female")),
    faceEmotion = factor(faceEmotion, levels = c("Excited", "Calm", "Neutral")),
    subID = factor(subID, unique(subID)))

longGivingdata = longGivingdata %>% dplyr::filter(!is.na(response))
```

## Sample size

Main analyses (!is.na(subID))

```{r sample size main}
print("n_total:"); longGivingdata %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata %>%
  dplyr::filter(culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata %>%
  dplyr::filter(culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```
Supple analyses (exclude_sd != 1)

```{r sample size exclude sd}
print("n_total:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1) %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1, culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1, culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```

Supple analyses (exclude_age != 1)

```{r sample size exclude age}
print("n_total:"); longGivingdata %>%
  dplyr::filter(exclude_age != 1) %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata %>%
  dplyr::filter(exclude_age != 1, culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata %>%
  dplyr::filter(exclude_age != 1, culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```

Supple analyses (exclude_sd != 1 & exclude_age != 1)

```{r sample size exclude age sd}
print("n_total:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1 & exclude_age != 1) %>%
  dplyr::summarise(n = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_tw:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1, exclude_age != 1, culture == "TN") %>%
  dplyr::summarise(n_tw = dplyr::n_distinct(subID)) %>% 
  pull()

print("n_ea:"); longGivingdata %>%
  dplyr::filter(exclude_sd != 1, exclude_age != 1, culture == "EA") %>%
  dplyr::summarise(n_ea = dplyr::n_distinct(subID)) %>% 
  pull()
```

\newpage

## Visualizations

```{r plot three-way, message = FALSE, fig.width = 10, fig.height = 7}

longGivingdata2 <- longGivingdata %>% dplyr::mutate(
  culture = if_else(culture == "EA", "European American", "Taiwanese")) %>%
  dplyr::rename(Culture = culture) %>%
  dplyr::mutate(
    mood = factor(mood,
                  labels = c("Neutral", "HAP", "HAN"),
                  levels = c("Neutral", "HAP", "HAN")))
ggplot(
  longGivingdata2 %>% 
    group_by(subID, mood, faceEmotion, Culture) %>% 
    summarise(response = mean(response, na.rm = T)) %>%
    group_by(faceEmotion, mood, Culture) %>%
    summarise(mean = mean(response, na.rm = T),
              SD = sd(response, na.rm = T),
              SE = sd(response, na.rm = T)/sqrt(n())), 
  aes(faceEmotion, mean, fill = Culture)) + 
  facet_grid(~mood)+
  scale_fill_manual(
    values = c("European American"="#F49070", "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1)+
  xlab("Facial Expression") +
  ylab("Amount Given (Raw)") +
  ggtitle("Amount Given by Mood Condition and Responder's Facial Expression") 

```

\newpage

```{r plot two-ways, message = FALSE, fig.width = 10, fig.height = 15}

p1 <- ggplot(longGivingdata2 %>%
               group_by(subID, mood, Culture) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(mood, Culture) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(mood, mean, fill = Culture)) + 
  scale_fill_manual(values = 
                      c("European American"="#F49070", 
                        "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Mood") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by Mood Condition") 

p2 <- ggplot(longGivingdata2 %>%
               group_by(subID, faceEmotion, Culture) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(faceEmotion, Culture) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(faceEmotion, mean, fill = Culture)) + 
  scale_fill_manual(values = 
                      c("European American"="#F49070", 
                        "Taiwanese"="#52B2CF")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Facial Expression") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by faceEmotion Condition") 

p3 <- ggplot(longGivingdata2 %>%
               group_by(subID, faceEmotion, mood) %>% 
               summarise(response = mean(response, na.rm = T)) %>%
               group_by(faceEmotion, mood) %>%
               summarise(
                 mean = mean(response, na.rm=T),
                 SD = sd(response, na.rm = T),
                 SE = sd(response, na.rm = T)/sqrt(n())), 
             aes(mood, mean, fill = faceEmotion)) + 
  scale_fill_manual(values = 
                      c("Neutral"="grey", 
                        "Excited"="lightyellow",
                        "Calm"="lightblue")) +
  geom_bar(stat='identity', position='dodge') +
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), 
                position = position_dodge(0.9), width = 0.1) +
  xlab("Mood") +
  ylab("Amount Given (Ipsatized)") +
  ggtitle("Amount Given by faceEmotion Condition") 

p1 + p2 + p3 +
  patchwork::plot_layout(
    ncol = 1
  )

```

\newpage

## Analyses

```{r main three-way analysis}

aov_analysis(
  formula = response ~ mood*culture*faceEmotion + 
    Error(subID/(mood*faceEmotion)),
  data = longGivingdata,
  filter_condition1 = sensitivity_analyses)

```
