---
title: "ia_study1_computeMeasures"
author: ""
date: "`r Sys.Date()`"
output: pdf_document
---

# Admin (Packages & Custom Functions)

```{r setup}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
source("https://raw.githubusercontent.com/vyqlua/avi_functions/refs/heads/main/ipsatize_fn.R")
```

```{r function for calculating alpha for sensitivity datasets, echo = FALSE}

# custom function for calculating alphas

all_alphas <- function(data = data, items, constructs, 
                       sensitivity = sensitivity_analyses) {
  reliability_sensitivity <- data.frame()
  cultures <- c("cultureEA == 1 | cultureEA == 0", 
                "cultureEA == 1", "cultureEA == 0")
  cultures_names <- c("overall", "EA", "TN")
  for (j in 1:3) {
    culturedata <- data %>% dplyr::filter(
      eval(parse(text = cultures[j])))
  # Iterate over each sensitivity analysis condition
  for (i in 1:length(sensitivity)) {
    currentdata <- tryCatch({
      culturedata %>% dplyr::filter(
        eval(parse(text = sensitivity[i])))
    }, error = function(e) {
      return(NULL) # Return NULL if error in filtering
    })
    # Proceed only if currentdata is not NULL
    if (!is.null(currentdata)) {
      reliab_list <- lapply(items, function(x) {
        cols <- unlist(strsplit(x, ",\\s*")) # Split into individual columns
        # Check if the required columns are all present and have variance
        if (
          all(cols %in% names(currentdata)) && 
          any(sapply(currentdata[cols], var, na.rm = TRUE) > 0)) 
          {
          alpha_res <- psych::alpha(currentdata %>% 
                                      dplyr::select(all_of(cols)), 
                                    check.keys = FALSE)
          return(data.frame(alpha = alpha_res$total$raw_alpha %>% 
                              round(2)))
        } 
        else {
          return(data.frame(alpha = NA)) 
          # Return NA if not all columns are present or no variance
        }
      })
      # Combine alpha values for current sensitivity analysis into a dataframe
      reliab_df <- do.call(rbind, reliab_list)
      reliab_df$construct <- constructs
      reliab_df$dataframe <- sensitivity[i]
      reliab_df$culture <- cultures_names[j]
      # Combine with the overall results
      reliability_sensitivity <- rbind(reliability_sensitivity, reliab_df)
    }
  }
    }
  return(reliability_sensitivity %>%
           pivot_wider(names_from = dataframe,
                       values_from = alpha) %>%
  dplyr::mutate(construct = paste(construct, culture, sep = "_")) %>%
    dplyr::select(-culture))
}

```
```{r create list for specifying arguments to filter additional exclusion criteria easily, echo = FALSE}

sensitivity_analyses <- c("!is.na(subID)",
  "exclude_age != 1", "exclude_sd != 1", 
  "exclude_age != 1 & exclude_sd != 1")


sensitivity_analyses_i <- c("!is.na(subID)", "exclude_age != 1")

```

\newpage

# Load Data

```{r load data, message = FALSE}
data <- read_csv("ia_study1_anon_data.csv")
data <- data[ , -1]
```

\newpage

# Ten Item Personality Inventory (TIPI)
  
Next, we compute the composite scores of the participant-level TIPI variables. Specifically, we calculate:
  
1. participant's extraversion `tipi_ex`
  + `tipi_1` (Extraverted, enthusiastic), `tipi_6` (reversed; Reserved, quiet)
2. participant's agreeableness, `tipi_a` 
  + `tipi_2` (reversed; Critical, quarrelsome), `tipi_7` (Sympathetic, warm)
3. participant's conscientiousness, `tipi_c`
  + `tipi_3` (Dependable, self-disciplined), `tipi_8` (reversed; Disorganized, careless)
4. participant's emotoinal stability, `tipi_es`
  + `tipi_4` (reversed; Anxious, easily upset), `tipi_9` (Calm, emotionally stable)
5. participant's openness to experience, `tipi_o`
  + `tipi_5` (Open to new experiences, complex), `tipi_10` (reversed; Conventional, uncreative)
  
```{r compute TIPI variables}

# compute tipi variables
data <- data %>% 
  rowwise() %>%
  dplyr::mutate( # reverse code tipi items
    tipi_6r = 8 - tipi_6,
    tipi_2r = 8 - tipi_2,
    tipi_8r = 8 - tipi_8,
    tipi_4r = 8 - tipi_4,
    tipi_10r = 8 - tipi_10
    ) %>%
  dplyr::mutate( # calculate tipi_ex, tipi_a, tipi_c, tipi_es, and tipi_o
    tipi_ex = mean(c(tipi_1, tipi_6r), na.rm = T),
    tipi_a = mean(c(tipi_2r, tipi_7), na.rm = T),
    tipi_c = mean(c(tipi_3, tipi_8r), na.rm = T),
    tipi_es = mean(c(tipi_4r, tipi_9), na.rm = T),
    tipi_o = mean(c(tipi_5, tipi_10r), na.rm = T)
    ) %>%
  ungroup()

```

```{r TIPI correlations}

data %>%
  dplyr::select("tipi_1", "tipi_6r", 
                 "tipi_2r", "tipi_7",
                 "tipi_3", "tipi_8r",
                 "tipi_4r", "tipi_9",
                 "tipi_5", "tipi_10r") %>% 
  cor(use = "pairwise.complete.obs") %>%
  round(2)

# European American
data %>% dplyr::filter(cultureEA == 1) %>%
  dplyr::select("tipi_1", "tipi_6r", 
                 "tipi_2r", "tipi_7",
                 "tipi_3", "tipi_8r",
                 "tipi_4r", "tipi_9",
                "tipi_5", "tipi_10r") %>% 
  cor(use = "pairwise.complete.obs") %>%
  round(2)

# Taiwanese
data %>% dplyr::filter(cultureEA == 0) %>%
  dplyr::select("tipi_1", "tipi_6r", 
                 "tipi_2r", "tipi_7",
                 "tipi_3", "tipi_8r",
                 "tipi_4r", "tipi_9",
                 "tipi_5", "tipi_10r")%>% 
  cor(use = "pairwise.complete.obs") %>%
  round(2)

```

\newpage

# Interpersonal Reativity Index (IRI)
  
Next, we compute the composite scores of the participant-level IRI variables. Specifically, we calculate:
  
1. participant's perspective-taking `iri_pt`
  + calculated by averaging `iri3`, `iri8`, `iri11`, `iri15`, `iri21`, `iri25`, & `iri28`
2. participant's fantasy, `iri_fs` 
  + calculated by averaging  `iri1`, `iri5`, `iri7`, `iri12`, `iri16`, `iri23`, & `iri26`
3. participant's empathetic concern, `iri_ec`
  + calculated by averaging  `iri2`, `iri4`, `iri9`, `iri14`, `iri18`, `iri20`, & `iri22`
4. participant's personal distress, `iri_pd`
  + calculated by averaging `iri6`, `iri10`, `iri13`, `iri17`, `iri19`, `iri24`, & `iri27`
  
  
```{r compute IRI variables}

# compute iri variables
data <- data %>% 
  rowwise() %>%
  dplyr::mutate( # reverse code iri items
    iri3r = 6 - iri3,
    iri4r = 6 - iri4,
    iri7r = 6 - iri7,
    iri12r = 6 - iri12,
    iri13r = 6 - iri13,
    iri14r = 6 - iri14,
    iri15r = 6 - iri15,
    iri18r = 6 - iri18,
    iri19r = 6 - iri19,
    ) %>%
  dplyr::mutate( # calculate iri_pt, iri_fs, iri_ec, iri_pd
    iri_pt = mean(
      c(iri3r, iri8, iri11, iri15r, iri21, iri25, iri28), na.rm = T),
    iri_fs = mean(
      c(iri1, iri5, iri7r, iri12r, iri16, iri23, iri26), na.rm = T),
    iri_ec = mean(
      c(iri2, iri4r, iri9, iri14r, iri18r, iri20, iri22), na.rm = T),
    iri_pd = mean(
      c(iri6, iri10, iri13r, iri17, iri19r, iri24, iri27), na.rm = T)
    ) %>%
  ungroup()
```

```{r IRI cronbach alphas}

reliab_iri <- c("iri3r, iri8, iri11, iri15r, iri21, iri25, iri28", 
              "iri1, iri5, iri7r, iri12r, iri16, iri23, iri26",
              "iri2, iri4r, iri9, iri14r, iri18r, iri20, iri22", 
              "iri6, iri10, iri13r, iri17, iri19r, iri24, iri27")

reliab_iri_names <- c("iri_pt", "iri_fs", "iri_ec", "iri_pd")

all_alphas(data, items = reliab_iri, constructs = reliab_iri_names, 
           sensitivity = sensitivity_analyses)

```
  
\newpage

# AVI
  
Now, we compute the composite scores of the participant-level AVI variables. 
  
```{r rename AVI variables}

avi_items <-  c( 
  "1_10" = ".sleepy",
  "1_1"  = ".enthusiastic", 
  "1_2"  = ".astonished",
  "1_3"  = ".nervous",
  "1_4"  = ".dull",
  "1_5"  = ".quiet",
  "1_6"  = ".relaxed",
  "1_7"  = ".excited", 
  "1_8"  = ".surprised",
  "1_9"  = ".elated", 
  "2_10" = ".fearful",
  "2_1"  = ".still",
  "2_2"  = ".lonely",
  "2_3"  = ".strong",
  "2_4"  = ".passive",
  "2_5"  = ".content",
  "2_6"  = ".sluggish",
  "2_7"  = ".inactive",
  "2_8"  = ".sad",
  "2_9"  = ".euphoric", 
  "3_10" = ".serene",
  "3_1"  = ".happy",
  "3_2"  = ".idle",
  "3_3"  = ".calm",
  "3_4"  = ".unhappy",
  "3_5"  = ".aroused",
  "3_6"  = ".hostile",
  "3_7"  = ".satisfied",
  "3_8"  = ".rested",
  "3_9"  = ".peaceful",
  "4_1"  = ".noemotion",
  "4_2"  = ".energetic",
  "4_3"  = ".ashamed",
  "4_4"  = ".disgusted",
  "4_5"  = ".stressed",
  "4_6"  = ".guilty",
  "4_7"  = ".contemptuous",
  "4_8"  = ".fatigued",
  "4_9"  = ".angry")

names(data) <- names(data) |>
  str_replace(paste0(names(avi_items), collapse = "|"),
              avi_items[str_extract(names(data), paste(names(avi_items), collapse="|"))])

```

```{r calculate actual AVI}

# actual affect
data <- ipsatize_avi(data, 
                     item_stem = "r.",
                     remove = c("euphoric", "contemptuous", "angry"), 
                     maximizing_pos = TRUE)
glimpse(avi_codebook)

```

```{r calculate ideal AVI}

# actual affect
data <- ipsatize_avi(data, 
                     item_stem = "i.",
                     remove = c("euphoric", "contemptuous", "angry"),
                     maximizing_pos = TRUE)
glimpse(avi_codebook)

```

```{r AVI cronbach alphas}

# calculate cronbach alpha for HAP and LAP

reliab_avi <- c("r.enthusiastic, r.excited, r.elated", 
                "r.relaxed, r.calm, r.peaceful, r.serene",
                "i.enthusiastic, i.excited, i.elated",
                "i.relaxed, i.calm, i.peaceful, i.serene")

reliab_avi_names <- c("rHAP", "rLAP", "iHAP", "iLAP")

all_alphas(data, items = reliab_avi, constructs = reliab_avi_names, 
           sensitivity = sensitivity_analyses)

```


\newpage

# Ipsatized giving scores  
  
Now, we compute the ipsatized scores of the trials. Alike the AVI variables, we calculate this by converting the amount of money given using this formula: `ipsatized score = (raw amoung given - individuals' mean amount given across all trials) / (individuals' sd across the amount of money given across all trials)`
  
```{r compute ipsatized giving scores}

# compute ipsatized giving scores
data <- data %>% 
  rowwise() %>%
  dplyr::mutate( # create intermediate variables for calculating ipsatize scores
    givingMean = mean(
      c_across(matches("^raw[1-9][1-9]*[0]*$")), na.rm = TRUE),
    givingSd = sd(
      c_across(matches("^raw[1-9][1-9]*[0]*$")), na.rm = TRUE)) %>%
  dplyr::mutate( # create ipsatized item scores
    across(matches("^raw[1-9][1-9]*[0]*$"), 
           ~ as.numeric((.x - givingMean) / givingSd),
           .names = "{.col}_i")) %>%
  ungroup()

```

\newpage

# Ipsatized trait rating scores  
  
Finally, we compute the ipsatized scores of the trait ratings for the faces (items that start with `trait`, `vale`, and `arou`). 

All participants rated the faces on numerous traits. Specifically, they responded to the prompt "To what extent is this person..." (e.g., "Competent", "Trustworthy", etc.; 1 = *Not at all*, 4 = *Moderately*, 7 = *Extremely*) and how positive ("*How <u>negative - positive</u> do you feel when you see this face?*"; 1 = *Extremely negative*, 7 = *Extremely positive*) and aroused ("*How <u>not-aroused - aroused</u> do you feel when you see this face? Aroused means activated, charged, alert, or energized physically and mentally.*"; 1 = *Not at all aroused*, 7 = *Extremely aroused*) they feel when they see the face. For the repeated ratings, we only include the first rating they provide.

Alike the AVI and giving variables, we calculate this by converting the ratings given using this formula: `ipsatized score = (raw rating - individuals' mean rating across all traits and faces) / (individuals' sd rating across all traits and faces)`. Note that for valence (`vale`) and arousal (`arou`) ratings, they are ipsatized within the valence and arousal ratings only (i.e., `ipsatized valence = (raw valence rating - individuals' mean rating of valence across all faces) / (individuals' sd of valence across all faces)`.
  
```{r compute ipsatized trait rating scores}

# compute ipsatized trait rating scores
data <- data %>% 
  rowwise() %>%
  dplyr::mutate( # create intermediate variables for calculating ipsatize scores
    traitRatingMean = mean(
      c_across(matches("^trait[1-9][0-9]*_")), na.rm = TRUE),
    traitRatingSd = sd(
      c_across(matches("^trait[1-9][0-9]*_")), na.rm = TRUE),
    valeRatingMean = mean(
      c_across(matches("^vale[1-9][0-9]*$")), na.rm = TRUE),
    valeRatingSd = sd(
      c_across(matches("^vale[1-9][0-9]*$")), na.rm = TRUE),
    arouRatingMean = mean(
      c_across(matches("^arou[1-9][0-9]*$")), na.rm = TRUE),
    arouRatingSd = sd(
      c_across(matches("^arou[1-9][0-9]*$")), na.rm = TRUE)) %>%
  dplyr::mutate( 
    # create ipsatized item scores
    across(matches("^trait[1-9][0-9]*_"), 
           ~ as.numeric((.x - traitRatingMean) / traitRatingSd),
           .names = "{.col}_i")) %>%
  dplyr::mutate( # create ipsatized item scores
    across(matches("^vale[1-9][0-9]*$"), 
           ~ as.numeric((.x - valeRatingMean) / valeRatingSd),
           .names = "{.col}_i")) %>%
  dplyr::mutate( # create ipsatized item scores
    across(matches("^arou[1-9][0-9]*$"), 
           ~ as.numeric((.x - arouRatingMean) / arouRatingSd),
           .names = "{.col}_i")) %>%
  ungroup()

```

\newpage

# Save data computed frame 

```{r write csv}

write.csv(data, "ia_study1_anon_data_computed.csv")

```

## Descriptives

```{r descriptives function, message = FALSE}

# descriptives function
describe_all <- function(data, filter_condition1) {
  for (i in 1:length(filter_condition1)) {
      subset_data <- data %>% 
        filter(eval(parse(text = filter_condition1[i])))
   desc <- subset_data  %>% rowwise() %>%
    dplyr::mutate(
      avg_giving_amt = mean(
        c_across((starts_with("raw") & !contains("_Page.Submit")))),
      avg_giving_RT = mean(
        c_across((starts_with("raw") & contains("_Page.Submit"))))) %>% 
      dplyr::select(gender_nonfemale, sexualpref_nonhetero, ethn_nonmajority,
                    age, famises2_numbered, selfses2_numbered, 
                    tipi_ex, tipi_a, tipi_c, tipi_es, tipi_o,
                    iri_pt, iri_fs, iri_ec, iri_pd,
                    avg_giving_amt, avg_giving_RT,
                    rHAP, rLAP, iHAP, iLAP) %>%
     psych::describe(fast = TRUE, skew = FALSE)
  print(filter_condition1[i])
  print(desc)
  }
}

```

\newpage

```{r describe}
# Pooled data
describe_all(data = data, sensitivity_analyses)
```

\newpage

```{r describe EA}
# European American
describe_all(data = data %>% dplyr::filter(cultureEA == 1), sensitivity_analyses)
```

\newpage

```{r describe TN}
# Taiwanese
describe_all(data = data %>% dplyr::filter(cultureEA == 0), sensitivity_analyses)

```

