---
title: "Incidental Affect Image Test"
author: " "
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

\newpage

# Admin

```{r libraries, results = "hide", message = FALSE, warning = FALSE}

#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(brms)
library(performance)
library(bridgesampling)
library(patchwork)
source("https://raw.githubusercontent.com/vyqlua/avi_functions/refs/heads/main/ipsatize_fn.R")
conflicted::conflicts_prefer(dplyr::filter)
conflicted::conflicts_prefer(lmerTest::lmer)

```

# Data cleaning 

```{r load TN data}

# Taiwan Data

d_TN <- read.csv("raw_data/TN_ImageTest.csv", encoding = "UTF-8") %>%
  dplyr::filter(id != "TEST",
                Status == 0,
                IPAddress != "128.252.48.41",
                Finished == 1,
                consent1 == 1) %>%
  distinct(IPAddress, .keep_all = TRUE) %>%
  distinct(email, .keep_all = TRUE) %>%
  dplyr::select(-IPAddress, -starts_with("Location"), -starts_with("Recipient"), 
                -email, -id, -UserLanguage, -Q_DuplicateRespondent, 
                -(agre_screener:consent1)) %>%
  dplyr::mutate(Culture = "TN") %>%
  dplyr::select(StartDate:DistributionChannel, Culture, everything()) 

### NOTE: in qualtrics, arousal and valence question labels are switched.

d_TN <- d_TN %>% 
  dplyr::rename_with(
    ~ str_replace_all(.,
                      c("_arou" = "_VALE",
                        "_vale" = "_AROU"))) %>%
  dplyr::rename_with(
    ~ str_replace_all(.,
                      c("_AROU" = "_arou",
                        "_VALE" = "_vale")))

```

```{r load EA data}

# European American Data

d_EA <- read.csv("raw_data/EA_ImageTest.csv", encoding = "UTF-8") %>%
  dplyr::filter(id != "TEST",
                Status == 0,
                Finished == 1,
                consent1 == 1)  %>%
  distinct(IPAddress, .keep_all = TRUE) %>%
  distinct(id, .keep_all = TRUE) %>%
  dplyr::select(-IPAddress, -starts_with("Location"), -starts_with("Recipient"), 
                -email, -id, -UserLanguage, -Q_DuplicateRespondent, 
                -(prescreen_age:consent1)) %>%
  dplyr::mutate(Culture = "EA") %>%
  dplyr::select(StartDate:DistributionChannel, Culture, everything()) 

```

```{r merge}

# Merge

d <- rbind(d_EA, d_TN) %>%
  dplyr::mutate(
    dplyr::across(X1_neu_vale:age, as.numeric))%>%
  dplyr::rename_with(
    ~ str_replace_all(.,
                      c("1_10" = ".sleepy",
                        "1_1"  = ".enthusiastic", 
                        "1_2"  = ".astonished",
                        "1_3"  = ".nervous",
                        "1_4"  = ".dull",
                        "1_5"  = ".quiet",
                        "1_6"  = ".relaxed",
                        "1_7"  = ".excited", 
                        "1_8"  = ".surprised",
                        "1_9"  = ".elated", 
                        "2_10" = ".fearful",
                        "2_1"  = ".still",
                        "2_2"  = ".lonely",
                        "2_3"  = ".strong",
                        "2_4"  = ".passive",
                        "2_5"  = ".content",
                        "2_6"  = ".sluggish",
                        "2_7"  = ".inactive",
                        "2_8"  = ".sad",
                        "2_9"  = ".euphoric", 
                        "3_10" = ".serene",
                        "3_1"  = ".happy",
                        "3_2"  = ".idle",
                        "3_3"  = ".calm",
                        "3_4"  = ".unhappy",
                        "3_5"  = ".aroused",
                        "3_6"  = ".hostile",
                        "3_7"  = ".satisfied",
                        "3_8"  = ".rested",
                        "3_9"  = ".peaceful",
                        "4_1"  = ".noemotion",
                        "4_2"  = ".energetic",
                        "4_3"  = ".ashamed",
                        "4_4"  = ".disgusted",
                        "4_5"  = ".stressed",
                        "4_6"  = ".guilty",
                        "4_7"  = ".contemptuous",
                        "4_8"  = ".fatigued",
                        "4_9"  = ".angry")))

write.csv(d, "imageTestData.csv")

rm(d_EA, d_TN, d)

```


# Load data 

```{r load data}

d <- read.csv("imageTestData.csv") %>% dplyr::select(-"X")

```

# Sample Demographics

```{r sample demogs}

# European American
d %>% dplyr::filter(Culture == "EA") %>%
  summarize(Culture = "EA",
            M_age = mean(age, na.rm = T),
            SD_age = sd(age, na.rm = T),
            Female = sum(gender == "2", na.rm = T)/ n())

# TN
d %>% dplyr::filter(Culture == "TN") %>%
  summarize(Culture = "TN",
            M_age = mean(age, na.rm = T),
            SD_age = sd(age, na.rm = T),
            Female = sum(gender == "2", na.rm = T)/ n())

```


# AVI

```{r AVI calculation real affect}
d <- d %>% 
  ipsatize_avi("r.", 
               remove = c("euphoric", "contemptuous", "angry"), 
               full_avi = TRUE, 
               maximizing_pos = TRUE)
```

```{r AVI calculation ideal affect}
d <- d %>% 
  ipsatize_avi("i.", 
               remove = c("euphoric", "contemptuous", "angry"), 
               full_avi = TRUE, 
               maximizing_pos = TRUE) 
```

```{r plot avi, results = "hide"}

plot_avi(
  d %>% dplyr::select(Culture, rHAP:rMaxPos_ip, iHAP:iMaxPos_ip), 
  "Culture")

```

\newpage

# Continuous Valence & Arousal

```{r compute composite scores for vale and arou}

d <- d %>% dplyr::mutate(
  han_vale = dplyr::across(contains("_han_vale")) %>% rowMeans(),
  han_arou = dplyr::across(contains("_han_arou")) %>% rowMeans(),
  hap_vale = dplyr::across(contains("_hap_vale")) %>% rowMeans(),
  hap_arou = dplyr::across(contains("_hap_arou")) %>% rowMeans(),
  neu_vale = dplyr::across(contains("_neu_vale")) %>% rowMeans(),
  neu_arou = dplyr::across(contains("_neu_arou")) %>% rowMeans())

```

## Valence

### Plot

```{r plot valence, echo = FALSE}

d1 <- d %>% dplyr::select(ResponseId, Culture, han_vale:neu_arou)

d1_long <- d1 %>%
  pivot_longer(
    cols = han_vale:neu_arou,
    names_to = "dimension",
    values_to = "value"
  ) %>%
  filter(grepl("_vale$", dimension))

d1_summary <- d1_long %>%
  group_by(Culture, dimension) %>%
  summarise(mean_value = mean(value, na.rm = TRUE), 
            se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
            .groups = "drop")

ggplot() +
  geom_col(
    data = d1_summary,
    aes(x = dimension, y = mean_value, fill = Culture),
    width = 0.7
  ) +
  geom_jitter(
    data = d1_long,
    aes(x = dimension, y = value, color = Culture),
    width = 0.15,
    alpha = 0.4,
    size = 1.5
  ) +
  geom_errorbar(
    data = d1_summary,
    aes(
      x = dimension,
      ymin = mean_value - se,
      ymax = mean_value + se
    ),
    width = 0.2
  ) +
  facet_wrap(~ Culture) +
  labs(
    x = "Image Type",
    y = "Valence Rating"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  coord_cartesian(ylim = c(1, NA)) +
  scale_y_continuous(breaks = seq(1, 7, by = 1)) +
  scale_fill_manual(values = c("TN" = "#52B2CF", "EA" = "#F49070"))

rm(d1, d1_long, d1_summary)
```

\newpage

```{r plot valence ipsatized, echo = FALSE}

d_vale <- d %>% 
  dplyr::select(ResponseId, Culture, 
                contains("_vale"),
                -hap_vale, -han_vale, -neu_vale)

d_vale_long <- d_vale %>%
  pivot_longer(
    cols = -c(ResponseId, Culture),
    names_to = "dimension",
    values_to = "value"
  ) %>%
  dplyr::mutate(
    image_no = str_extract(dimension, "(?<=^X)[0-9]+"),
    affect = substr(dimension, nchar(dimension)-7, nchar(dimension)-5))

d_vale_long <- d_vale_long %>%
  group_by(ResponseId) %>%
  dplyr::mutate(
    value = (value - mean(value, na.rm = T)) / sd(value, na.rm = T)) %>%
  ungroup() 

d_vale_long <- d_vale_long %>%
  group_by(ResponseId, Culture, affect) %>%
  dplyr::summarize(value = mean(value)) %>%
  ungroup()

d1_summary <- d_vale_long %>%
  group_by(Culture, affect) %>%
  summarise(mean_value = mean(value, na.rm = TRUE), 
            se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
            .groups = "drop")

ggplot() +
  geom_col(
    data = d1_summary,
    aes(x = affect, y = mean_value, fill = Culture),
    width = 0.7
  ) +
  geom_jitter(
    data = d_vale_long,
    aes(x = affect, y = value, color = Culture),
    width = 0.15,
    alpha = 0.4,
    size = 1.5
  ) +
  geom_errorbar(
    data = d1_summary,
    aes(
      x = affect,
      ymin = mean_value - se,
      ymax = mean_value + se
    ),
    width = 0.2
  ) +
  facet_wrap(~ Culture) +
  labs(
    x = "Image Type",
    y = "Valence Rating (Ipsatized)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_manual(values = c("TN" = "#52B2CF", "EA" = "#F49070"))


rm(d_vale, d_vale_long, d1_summary)
```

\newpage

### By Image Type

```{r create long valence data for analysis, results = "hide"}

# create long valence data for analysis

d_vale <- d %>% 
  dplyr::select(ResponseId, Culture, 
                contains("_vale"),
                -hap_vale, -han_vale, -neu_vale)

d_vale_long <- d_vale %>%
  pivot_longer(
    cols = -c(ResponseId, Culture),
    names_to = "dimension",
    values_to = "value"
  ) %>%
  dplyr::mutate(
    image_no = str_extract(dimension, "(?<=^X)[0-9]+"),
    affect = substr(dimension, nchar(dimension)-7, nchar(dimension)-5))

# ipsatize valence ratings

d_vale_long <- d_vale_long %>%
  group_by(ResponseId) %>%
  dplyr::mutate(
    value_ip = (value - mean(value, na.rm = T)) / sd(value, na.rm = T)) %>%
  ungroup()

```

```{r analysis for valence by image type, message = FALSE}

# non-ip
rating_by_imagetype <- 
  lmer(value ~ affect + (1 | ResponseId) + (1 | image_no),
       data = d_vale_long,
       REML = FALSE) 

summary(rating_by_imagetype)
emmeans(rating_by_imagetype, pairwise ~ affect)

```

```{r analysis for valence by image type ipsatized, message = FALSE}

#ip
rating_by_imagetype_ip <- 
  lmer(value_ip ~ affect + (1 | image_no),
       data = d_vale_long,
       REML = FALSE) # removed (1 | responseID) since its ipsatized 

summary(rating_by_imagetype_ip)
emmeans(rating_by_imagetype_ip, pairwise ~ affect)

```

\newpage

### By Image Type * Culture

```{r analysis for valence by image type * culture, message = FALSE}

#non-ip

rating_by_imagetype_culture <- 
  lmer(value ~ affect * Culture + (1 | ResponseId) + (1 | image_no),
       data = d_vale_long,
       REML = FALSE) 

summary(rating_by_imagetype_culture)
emmeans(rating_by_imagetype_culture, pairwise ~ affect | Culture)
emmeans(rating_by_imagetype_culture, pairwise ~ Culture | affect)

```
```{r model comparison for valence by image type * culture}

print("nonip ratings"); r2(rating_by_imagetype); r2(rating_by_imagetype_culture)

```

\newpage

```{r analysis for valence by image type * culture ipsatized, message = FALSE}

# ip
rating_by_imagetype_culture_ip <- 
  lmer(value_ip ~ affect * Culture + (1 | image_no),
       data = d_vale_long,
       REML = FALSE) # removed (1 | responseID) since its ipsatized 

summary(rating_by_imagetype_culture_ip)
# emmeans(rating_by_imagetype_culture_ip, pairwise ~ affect | Culture)
emmeans(rating_by_imagetype_culture_ip, pairwise ~ Culture | affect)

```
```{r model comparison for valence by image type * culture ipsatized}

print("ip ratings"); r2(rating_by_imagetype_ip); r2(rating_by_imagetype_culture_ip)

```

```{r clean environment valence, echo = FALSE}
rm(d_vale, d_vale_long, 
   rating_by_imagetype, rating_by_imagetype_ip, 
   rating_by_imagetype_culture, rating_by_imagetype_culture_ip)
```

\newpage

## Arousal

### Plot

```{r plot arousal, echo = FALSE}

d1 <- d %>% dplyr::select(ResponseId, Culture, han_vale:neu_arou)

d1_long <- d1 %>%
  pivot_longer(
    cols = han_vale:neu_arou,
    names_to = "dimension",
    values_to = "value"
  ) %>%
  filter(grepl("_arou$", dimension))

d1_summary <- d1_long %>%
  group_by(Culture, dimension) %>%
  summarise(mean_value = mean(value, na.rm = TRUE), 
            se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
            .groups = "drop")

ggplot() +
  geom_col(
    data = d1_summary,
    aes(x = dimension, y = mean_value, fill = Culture),
    width = 0.7
  ) +
  geom_jitter(
    data = d1_long,
    aes(x = dimension, y = value, color = Culture),
    width = 0.15,
    alpha = 0.4,
    size = 1.5
  ) +
  geom_errorbar(
    data = d1_summary,
    aes(
      x = dimension,
      ymin = mean_value - se,
      ymax = mean_value + se
    ),
    width = 0.2
  ) +
  facet_wrap(~ Culture) +
  labs(
    x = "Image Type",
    y = "Arousal Rating"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  coord_cartesian(ylim = c(1, NA)) +
  scale_y_continuous(breaks = seq(1, 7, by = 1)) +
  scale_fill_manual(values = c("TN" = "#52B2CF", "EA" = "#F49070"))


rm(d1, d1_long, d1_summary)
```

\newpage

```{r plot arousal ipsatized, echo = FALSE}

d_arou <- d %>% 
  dplyr::select(ResponseId, Culture, 
                contains("_arou"),
                -hap_arou, -han_arou, -neu_arou)

d_arou_long <- d_arou %>%
  pivot_longer(
    cols = -c(ResponseId, Culture),
    names_to = "dimension",
    values_to = "value"
  ) %>%
  dplyr::mutate(
    image_no = str_extract(dimension, "(?<=^X)[0-9]+"),
    affect = substr(dimension, nchar(dimension)-7, nchar(dimension)-5))

d_arou_long <- d_arou_long %>%
  group_by(ResponseId) %>%
  dplyr::mutate(
    value = (value - mean(value, na.rm = T)) / sd(value, na.rm = T)) %>%
  ungroup()

d_arou_long <- d_arou_long %>%
  group_by(ResponseId, Culture, affect) %>%
  dplyr::summarize(value = mean(value)) %>%
  ungroup()

d1_summary <- d_arou_long %>%
  group_by(Culture, affect) %>%
  summarise(mean_value = mean(value, na.rm = TRUE), 
            se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
            .groups = "drop")

ggplot() +
  geom_col(
    data = d1_summary,
    aes(x = affect, y = mean_value, fill = Culture),
    width = 0.7
  ) +
  geom_jitter(
    data = d_arou_long,
    aes(x = affect, y = value, color = Culture),
    width = 0.15,
    alpha = 0.4,
    size = 1.5
  ) +
  geom_errorbar(
    data = d1_summary,
    aes(
      x = affect,
      ymin = mean_value - se,
      ymax = mean_value + se
    ),
    width = 0.2
  ) +
  facet_wrap(~ Culture) +
  labs(
    x = "Image Type",
    y = "Arousal Rating (Ipsatized)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_manual(values = c("TN" = "#52B2CF", "EA" = "#F49070"))


rm(d_arou, d_arou_long, d1_summary)
```

\newpage

### By Image Type

```{r create long arousal data for analysis}

d_arou <- d %>% 
  dplyr::select(ResponseId, Culture, 
                contains("_arou"),
                -hap_arou, -han_arou, -neu_arou)

d_arou_long <- d_arou %>%
  pivot_longer(
    cols = -c(ResponseId, Culture),
    names_to = "dimension",
    values_to = "value"
  ) %>%
  dplyr::mutate(
    image_no = str_extract(dimension, "(?<=^X)[0-9]+"),
    affect = substr(dimension, nchar(dimension)-7, nchar(dimension)-5))

# ipsatize arousal ratings

d_arou_long <- d_arou_long %>%
  group_by(ResponseId) %>%
  dplyr::mutate(
    value_ip = (value - mean(value, na.rm = T)) / sd(value, na.rm = T)) %>%
  ungroup()

```

```{r analysis for arousal by image type, message = FALSE}

arousal_by_imagetype <- 
  lmer(value ~ affect + (1 | ResponseId) + (1 | image_no),
       data = d_arou_long) 

summary(arousal_by_imagetype)
emmeans(arousal_by_imagetype, pairwise ~ affect)

```

```{r analysis for arousal by image type ipsatized, message = FALSE}

arousal_by_imagetype_ip <- 
  lmer(value_ip ~ affect + (1 | image_no),
       data = d_arou_long) 

summary(arousal_by_imagetype_ip)
emmeans(arousal_by_imagetype_ip, pairwise ~ affect)

```

\newpage

### By Image Type * Culture

```{r analysis for arousal by image type * culture}

arousal_by_imagetype_culture <- 
  lmer(value ~ affect * Culture + (1 | ResponseId) + (1 | image_no),
       data = d_arou_long) 

summary(arousal_by_imagetype_culture)
emmeans(arousal_by_imagetype_culture, pairwise ~ affect | Culture)
emmeans(arousal_by_imagetype_culture, pairwise ~ Culture | affect)

```
```{r model comparison for arousal by image type * culture}

print("nonip arousals"); r2(arousal_by_imagetype); r2(arousal_by_imagetype_culture)

```

\newpage

```{r analysis for arousal by image type * culture ipsatized, message = FALSE}

arousal_by_imagetype_culture_ip <- 
  lmer(value_ip ~ affect * Culture + (1 | image_no),
       data = d_arou_long) 

summary(arousal_by_imagetype_culture_ip)
#emmeans(arousal_by_imagetype_culture_ip, pairwise ~ affect | Culture)
emmeans(arousal_by_imagetype_culture_ip, pairwise ~ Culture | affect)

```
```{r model comparison for arousal by image type * culture ipsatized}

print("ip arousals"); r2(arousal_by_imagetype_ip); r2(arousal_by_imagetype_culture_ip)

```

```{r clean environment arousal, echo = FALSE}
rm(d_arou, d_arou_long, 
   arousal_by_imagetype, arousal_by_imagetype_ip, 
   arousal_by_imagetype_culture, arousal_by_imagetype_culture_ip)
```


\newpage

# Discrete Emotions

Discrete Emotions:
1 Angry
2 Disgusted
3 Afraid
4 Sad
5 Bored
6 Anxious
7 Tired
8 Calm
9 Happy
10 Excited
11 Surprised
12 Energized
13 Elated
14 Neutral
15 No Emotion


```{r fig.width = 10, echo = FALSE}

d1 <- d %>% dplyr::select(ResponseId, Culture, contains("_feel")) %>%
  dplyr::mutate(
    dplyr::across(contains("_feel"), 
                  ~ factor(.x, 
                           levels = 1:15,
                           labels = 
                             c(
                               "Angry",
                               "Disgusted", 
                               "Afraid",
                               "Sad",
                               "Bored",
                               "Anxious",
                               "Tired",
                               "Calm",
                               "Happy",
                               "Excited",
                               "Surprised",
                               "Energized",
                               "Elated",
                               "Neutral",
                               "NOEmotion"))))

d1_long <- d1 %>%
  pivot_longer(
    cols = ends_with("_feel"),
    names_to = "item",
    values_to = "emotion"
  ) %>%
  filter(!is.na(emotion)) %>%
  mutate(
    condition = case_when(
      str_detect(item, "_han_") ~ "han",
      str_detect(item, "_hap_") ~ "hap",
      str_detect(item, "_neu_") ~ "neu"
    )
  )

d1_counts <- d1_long %>%
  group_by(Culture, condition, emotion) %>%
  summarise(n = n(), .groups = "drop")

ggplot(d1_counts, aes(x = emotion, y = n, fill = Culture)) +
  geom_col(position = "dodge") +
  facet_wrap(~ condition, nrow = 1) +
  labs(
    x = "Reported Emotion",
    y = "Count"
  ) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 65, hjust = 1)
  ) + 
  ggtitle("Which emotion does this image make you feel?")

```

```{r fig.width = 10, echo = FALSE}

d1 <- d %>% dplyr::select(ResponseId, Culture, contains("_desc")) %>%
  dplyr::mutate(
    dplyr::across(contains("_desc"), 
                  ~ factor(.x, 
                           levels = 1:15,
                           labels = 
                             c(
                               "Angry",
                               "Disgusted", 
                               "Afraid",
                               "Sad",
                               "Bored",
                               "Anxious",
                               "Tired",
                               "Calm",
                               "Happy",
                               "Excited",
                               "Surprised",
                               "Energized",
                               "Elated",
                               "Neutral",
                               "NOEmotion"))))

d1_long <- d1 %>%
  pivot_longer(
    cols = ends_with("_desc"),
    names_to = "item",
    values_to = "emotion"
  ) %>%
  filter(!is.na(emotion)) %>%
  mutate(
    condition = case_when(
      str_detect(item, "_han_") ~ "han",
      str_detect(item, "_hap_") ~ "hap",
      str_detect(item, "_neu_") ~ "neu"
    )
  )

d1_counts <- d1_long %>%
  group_by(Culture, condition, emotion) %>%
  summarise(n = n(), .groups = "drop")

ggplot(d1_counts, aes(x = emotion, y = n, fill = Culture)) +
  geom_col(position = "dodge") +
  facet_wrap(~ condition, nrow = 1) +
  labs(
    x = "Reported Emotion",
    y = "Count"
  ) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 65, hjust = 1)
  ) + 
  ggtitle("Which emotion BEST describes this image?")
```

\newpage

# Individual Image Ratings (Raw Valence)

```{r HAN Val, echo = FALSE}

d_han <- d %>% dplyr::select(Culture, contains("_han_vale")) 

d_han_long <- d_han %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p1 <- ggplot(d_han_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Han Valence item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )  +
  scale_y_continuous(breaks = seq(1, 7, by = 1))


```

```{r Neu Val, echo = FALSE}

d_neu <- d %>% dplyr::select(Culture, contains("_neu_vale")) 

d_neu_long <- d_neu %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p2 <- ggplot(d_neu_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Neu Valence item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )  +
  scale_y_continuous(breaks = seq(1, 7, by = 1))

```

```{r HAP Val, echo = FALSE}

d_hap <- d %>% dplyr::select(Culture, contains("_hap_vale")) 

d_hap_long <- d_hap %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p3 <- ggplot(d_hap_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "HAP Valence item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )  +
  scale_y_continuous(breaks = seq(1, 7, by = 1))

```

```{r 3 Plots Raw Val, warning = FALSE, fig.width = 15}

p1 + p2 + p3 +
  patchwork::plot_layout(ncol = 3)

```


# Individual Image Ratings (Ipsatized Valence)

```{r Val Ip, echo = FALSE}

d_ip <- d %>%
  rowwise() %>%
  dplyr::mutate(
    vale_m =  mean(c_across(contains("X") & contains("_vale")), na.rm = TRUE),
    vale_sd =  sd(c_across(contains("X") & contains("_vale")), na.rm = TRUE)) %>% 
  ungroup() %>%
  rowwise() %>%
  dplyr::mutate(
    across(
      contains("X") & contains("_vale"),
      ~ (.x - vale_m) / vale_sd))

```

```{r HAN Val Ip, echo = FALSE}

d_han <- d_ip %>% dplyr::select(Culture, contains("_han_vale")) 

d_han_long <- d_han %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p1 <- ggplot(d_han_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Han Valence item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )


```

```{r Neu Val Ip, echo = FALSE}

d_neu <- d_ip %>% dplyr::select(Culture, contains("_neu_vale")) 

d_neu_long <- d_neu %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p2 <- ggplot(d_neu_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Neu Valence item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 

```

```{r HAP Val Ip, echo = FALSE}

d_hap <- d_ip %>% dplyr::select(Culture, contains("_hap_vale")) 

d_hap_long <- d_hap %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p3 <- ggplot(d_hap_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "HAP Valence item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 

```

```{r 3 Plots Ip Val, warning = FALSE, fig.width = 15}

p1 + p2 + p3 +
  patchwork::plot_layout(ncol = 3)

```

\newpage

# Individual Image Ratings (Raw Arousal)

```{r HAN Arou, echo = FALSE}

d_han <- d %>% dplyr::select(Culture, contains("_han_arou")) 

d_han_long <- d_han %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p1 <- ggplot(d_han_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Han Arousal item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )  +
  scale_y_continuous(breaks = seq(1, 7, by = 1))


```

```{r Neu Arou, echo = FALSE}

d_neu <- d %>% dplyr::select(Culture, contains("_neu_arou")) 

d_neu_long <- d_neu %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p2 <- ggplot(d_neu_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Neu Arousal item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )  +
  scale_y_continuous(breaks = seq(1, 7, by = 1))

```

```{r HAP Arou, echo = FALSE}

d_hap <- d %>% dplyr::select(Culture, contains("_hap_arou")) 

d_hap_long <- d_hap %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p3 <- ggplot(d_hap_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "HAP Arousal item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )  +
  scale_y_continuous(breaks = seq(1, 7, by = 1))

```

```{r 3 Plots Raw Arou, warning = FALSE, fig.width = 15}

p1 + p2 + p3 +
  patchwork::plot_layout(ncol = 3)

```


# Individual Image Ratings (Ipsatized Arousal)

```{r Arou Ip, echo = FALSE}

d_ip <- d_ip %>%
  rowwise() %>%
  dplyr::mutate(
    arou_m =  mean(c_across(contains("X") & contains("_arou")), na.rm = TRUE),
    arou_sd =  sd(c_across(contains("X") & contains("_arou")), na.rm = TRUE)) %>% 
  ungroup() %>%
  rowwise() %>%
  dplyr::mutate(
    across(
      contains("X") & contains("_arou"),
      ~ (.x - arou_m) / arou_sd))

```

```{r HAN Arou Ip, echo = FALSE}

d_han <- d_ip %>% dplyr::select(Culture, contains("_han_arou")) 

d_han_long <- d_han %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p1 <- ggplot(d_han_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Han Arousal item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 

```

```{r Neu Arou Ip, echo = FALSE}

d_neu <- d_ip %>% dplyr::select(Culture, contains("_neu_arou")) 

d_neu_long <- d_neu %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p2 <- ggplot(d_neu_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "Neu Arousal item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 

```

```{r HAP Arou Ip, echo = FALSE}

d_hap <- d_ip %>% dplyr::select(Culture, contains("_hap_arou")) 

d_hap_long <- d_hap %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "item",
    values_to = "value"
  )


p3 <- ggplot(d_hap_long, aes(x = item, y = value, color = Culture)) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.2, jitter.height = 0.2, dodge.width = 0.6),
    alpha = 0.05,
    size = 0.5
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.6),
    size = 3,
    shape = 18
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(width = 0.6),
    width = 0.2
  ) +
  theme_bw() +
  labs(
    x = "HAP Arousal item",
    y = "Rating",
    color = "Culture"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 

```

```{r 3 Plots Ip Arou, warning = FALSE, fig.width = 15}

p1 + p2 + p3 +
  patchwork::plot_layout(ncol = 3)

```

\newpage

# Create Data Frame: Ratings by image

```{r, results = "hide"}

d_image_nonip <- d %>%
  dplyr::select(ResponseId, Culture, X1_neu_vale:X48_neu_desc) %>%
  pivot_longer(cols = X1_neu_vale:X48_neu_desc,
               names_to = "variable",
               values_to = "value") %>%
  dplyr::mutate(image_no = str_extract(variable, "(?<=^X)[0-9]+"),
                image_type = substr(
                  variable, nchar(variable)-7, nchar(variable)-5),
                rating_type = substr(
                  variable, nchar(variable)-3, nchar(variable))) %>%
  dplyr::select(ResponseId, Culture, image_type, 
                image_no, rating_type, value) %>%
  pivot_wider(id_cols = c(ResponseId, Culture, image_type, image_no),
              names_from = "rating_type",
              values_from = "value") %>%
  dplyr::mutate(feel = factor(feel, 
                              levels = 1:15,
                              labels = 
                                c("f_Angry", "f_Disgusted", "f_Afraid", 
                                  "f_Sad", "f_Bored", "f_Anxious", "f_Tired", 
                                  "f_Calm", "f_Happy", "f_Excited", 
                                  "f_Surprised", "f_Energized", 
                                  "f_Elated", "f_Neutral", "f_NOEmotion")),
                desc = factor(desc, 
                              levels = 1:15,
                              labels = 
                                c("d_Angry", "d_Disgusted", "d_Afraid", 
                                  "d_Sad", "d_Bored", "d_Anxious", "d_Tired", 
                                  "d_Calm", "d_Happy", "d_Excited", 
                                  "d_Surprised", "d_Energized", 
                                  "d_Elated", "d_Neutral", "d_NOEmotion"))
                ) %>%
  dplyr::mutate(feel = as.character(feel),
                desc = as.character(desc),
                value = 1,
                value2 = 1) %>%
  pivot_wider(id_cols = c(ResponseId, Culture, image_type, image_no,
                          vale, arou, desc, value2),
              names_from = "feel",
              values_from = "value",
              values_fill = 0) %>%
  pivot_wider(id_cols = c(ResponseId, Culture, image_type, image_no, 
                          vale, arou,
                          f_Angry, f_Disgusted, f_Afraid, f_Sad,
                          f_Bored, f_Anxious, f_Tired, f_Calm,
                          f_Happy, f_Excited, f_Surprised, f_Energized, 
                          f_Elated, f_Neutral, f_NOEmotion),
              names_from = "desc",
              values_from = "value2",
              values_fill = 0) %>%
  dplyr::select(ResponseId:f_NOEmotion, 
                d_Angry, d_Disgusted, d_Afraid, d_Sad,
                d_Bored, d_Anxious, d_Tired, d_Calm,
                d_Happy, d_Excited, d_Surprised, d_Energized, 
                d_Elated, d_Neutral, d_NOEmotion)


d_image_ip <- d_ip %>%
  dplyr::select(ResponseId, Culture, X1_neu_vale:X48_neu_desc) %>%
  pivot_longer(cols = X1_neu_vale:X48_neu_desc,
               names_to = "variable",
               values_to = "value") %>%
  dplyr::mutate(
    image_no = str_extract(variable, "(?<=^X)[0-9]+"),
    image_type = substr(
      variable, nchar(variable)-7, nchar(variable)-5),
    rating_type = paste0(
      substr(variable, nchar(variable)-3, nchar(variable)), "_ip")) %>%
  dplyr::select(
    ResponseId, Culture, image_type, image_no, rating_type, value) %>%
  pivot_wider(id_cols = c(ResponseId, Culture, image_type, image_no),
              names_from = "rating_type",
              values_from = "value") %>%
  dplyr::select(-c("feel_ip", "desc_ip"))

d_image <- merge(d_image_nonip, d_image_ip,
                 by = c("ResponseId", "Culture", "image_type", "image_no"))

rm(d_image_nonip, d_image_ip)

```

```{r, results = "hide"}

d_image_csv <- d_image %>% 
  group_by(Culture, image_type, image_no) %>%
  dplyr::mutate(
    n = n(),
    vale = mean(vale, na.rm = T), vale_sd = psych::SD(vale, na.rm = T),
    arou = mean(arou, na.rm = T), arou_sd = psych::SD(arou, na.rm = T),
    vale_ip = mean(vale_ip, na.rm = T), vale_ip_sd = psych::SD(vale_ip, na.rm = T),
    arou_ip = mean(arou_ip, na.rm = T), arou_ip_sd = psych::SD(arou_ip, na.rm = T),
  ) %>%
  dplyr::mutate(
    dplyr::across(contains("f_"), 
                  ~ mean(.x) * n())) %>%
  dplyr::mutate(
    dplyr::across(contains("d_"), 
                  ~ mean(.x) * n())) %>%
  dplyr::select(Culture, image_type, image_no, n, 
                vale, vale_sd, arou, arou_sd,
                vale_ip, vale_ip_sd, arou_ip, arou_ip_sd,
                everything(), -ResponseId) %>%
  dplyr::distinct() %>%
  dplyr::arrange(image_type, image_no, Culture)

#write.csv(d_image_csv, "d_imagetest.csv")

```

